An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-12 scagnostics.Rmd
findings bullet points
Remark added.

\textcolor{red}{Double challenging: fine structure + (coherent) noise}

@@

>>>>

\textcolor{red}{Double challenging: fine structure + (coherent) noise}
\textcolor{red}{simple standard guided tour does not find pipe easily with holes index, did not try brute force approach used with TIC index yet}

@@

<!--
- First example
    - Automatically find the functional relationship between three parameters
- Second example
    - Stronger relationship between already nonlinearly associated variables, when additional variable is incorporated
    - 
-->
